HMM Model

### 2020-11-14 manuscript/hmm.Rmd
Added first wave checks to HMM

@@

@@

@@

>>>>

## Treatments + age + sex + hospital, first wave only

```{r trt_group_m3_fw}
serie_data_fw <- serie_data %>% filter(first_wave)
simple_initial_states_fw <- serie_data_fw %>% filter(.time == 1) %>% arrange(.serie) %>% pull(.observed)

trt_group_m3_fw <- brmshmmdata(trt_group_m3_formula, serie_data_fw, 
                  simple_rate_data, trt_group_m1_hidden_state_data, simple_initial_states_fw, prior = trt_group_m1_prior,
                  observed_state_data = trt_group_m1_observed_state_data)

trt_group_m3_fw_fit <- brmhmm(trt_group_m3_fw, cache_file = paste0(cache_dir,"/trt_group_m3_fw.rds"), init = 0.1, control = default_control, iter = 1200)

summary(trt_group_m3_fw_fit$brmsfit)
```

```{r}
hmm_hypothesis_res_list[["trt_group_m3_fw"]] <-  evaluate_all_treatment_hypotheses(trt_group_m3_fw_fit, model_subgroup = "simple_group", adjusted ="all treatments, supportive, age, sex, hospital, first_wave", model_check = "OK", cl = cl)
```

```{r}
if(do_pp_checks) {
  do_common_pp_checks(trt_group_m3_fw_fit)
}
```

@@

## Treatment + age + sex + hospital + comorbidities, first wave

```{r trt_group_m4_fw}
trt_group_m4_fw <- brmshmmdata(trt_group_m4_formula, serie_data_fw, 
                  simple_rate_data, trt_group_m1_hidden_state_data, simple_initial_states_fw, prior = trt_group_m1_prior,
                  observed_state_data = trt_group_m1_observed_state_data)

trt_group_m4_fw_fit <- brmhmm(trt_group_m4_fw, cache_file = paste0(cache_dir,"/trt_group_m4_fw.rds"), init = 0.1, control = default_control, iter = 1200)

summary(trt_group_m4_fw_fit$brmsfit)
```

```{r}
hmm_hypothesis_res_list[["trt_group_m4_fw"]] <-  evaluate_all_treatment_hypotheses(trt_group_m4_fw_fit, model_subgroup = "simple_group", adjusted ="all treatments, supportive, age, sex, hospital, comorbidities, first_wave", model_check = "OK", cl = cl)
```

@@

## Treatments + age + sex + hospital, first_Wave

```{r trt_rate_m3_fw}
trt_rate_m3_fw <- brmshmmdata(trt_rate_m3_formula, serie_data_fw, 
                  trt_rate_m1_rate_data, trt_rate_m1_hidden_state_data, simple_initial_states_fw, prior = trt_rate_m1_prior,
                  observed_state_data = trt_rate_m1_observed_state_data)

trt_rate_m3_fw_fit <- brmhmm(trt_rate_m3_fw, cache_file = paste0(cache_dir,"/trt_rate_m3_fw.rds"), init = 0.1, control = default_control, iter = 1500)

summary(trt_rate_m3_fw_fit$brmsfit)
```

```{r}
hmm_hypothesis_res_list[["trt_rate_m3_fw"]] <-  evaluate_all_treatment_hypotheses(trt_rate_m3_fw_fit, model_subgroup = "simple_rate", adjusted ="all treatments, supportive, age, sex, hospital, first_wave", model_check = "OK", cl = cl)
```

```{r}
if(do_pp_checks) {
  do_common_pp_checks(trt_rate_m3_fw_fit)
}
```

@@

## Treatments + age + sex + hospital, first wave

```{r c_trt_m3_fw}
complex_initial_states_fw <- serie_data_fw %>% filter(.time == 1) %>% arrange(.serie) %>% pull(.observed) %>% paste0(., "_worsening")

c_trt_m3_fw <- brmshmmdata(trt_group_m3_formula, serie_data_fw, 
                  complex_rate_data, complex_hidden_state_data, complex_initial_states_fw, prior = trt_group_m1_prior,
                  observed_state_data = base_observed_state_data)

c_trt_m3_fw_fit <- brmhmm(c_trt_m3_fw, cache_file = paste0(cache_dir,"/c_trt_m3_fw.rds"), init = 0.1, control = default_control, iter = 1200)

summary(c_trt_m3_fw_fit$brmsfit)
```

```{r}
hmm_hypothesis_res_list[["c_trt_rate_m3_fw"]] <- evaluate_all_treatment_hypotheses(c_trt_m3_fw_fit, model_subgroup = "complex_group", adjusted ="all treatments, supportive, age, sex, hospital, first_wave", model_check = "OK", cl = cl)
